Globally-centered autocovariances in MCMC

### 2020-08-28 Paper/main.tex
Layer-3

\onehalfspacing
\begin{abstract}
Autocovariances are the fundamental quantity in many features of Markov chain Monte Carlo (MCMC) simulations with autcorrelation function (ACF) plots being often used as a visual tool to ascertain the performance of a Markov chain. Unfortunately, for slow mixing Markov chains, the empirical autocovariance can highly underestimate the truth. For multiple chain MCMC sampling,  we propose a globally-centered estimator of autocovariance function (G-ACvF) that pools information from all Markov chains. G-ACvF is also shown to correct the negative bias of single chain empirical autocovariance. We show the impact of this improved estimator in three aspects: (1) ACF plots, (2) estimates of the Monte Carlo asymptotic covariance matrix, and (3) estimates of the effective sample size. We have established the strong consistency of our improved asymptotic variance estimator, and obtained its large sample bias and variance.
\end{abstract}

@@

In this section we consider three different target distributions and sample $m$ parallel Markov chains using MCMC methods to experimentally analyse the performance of our globally-centered estimators. We will make the following three comparisons - (1) A-ACF vs G-ACF through ACrF plots; (2) A-SVE vs G-SVE; (3) $\widehat{\textrm{ESS}}_G$ vs $\widehat{\textrm{ESS}}_A$. The quality of estimation of $\Sigma$ is studied by coverage probabilities of a $95 \%$ Wald  confidence interval in cases where the true mean $\mu$ is known. The convergence of local and global estimators of $\Sigma$ and $\widehat{\textrm{ESS}}$ as $n$ increases is studied through two types of running plots (1) logarithm of Frobenius norm of estimated $\Sigma$, and (2) logarithm of estimated ESS/$mn$. In all the examples we are interested in estimating the mean of the stationary distribution $\mu$, so $g$ is the identity function. The batch size $b_n$ is obtained from the function \texttt{batchSize} from \texttt{R} package \texttt{mcmcse} \citep{mcmcse}.

@@

\begin{table}[htbp]
    \centering
    \small
    \begin{tabular}{|c|ccccc|}
    \hline
$n$  &  1000  & 5000  & 10000  & 50000  & 100000 \\  \hline
A-SV  &    0.710 & 0.843 & .885 & .928 & .944 \\ 
G-SV  &    0.956 & 0.937 & .924 & .945 & .952 \\ \hline
    \end{tabular}
    \caption{VAR(1). Coverage probabilities at $95 \%$ nominal level using A-SVE and G-SVE.}
    \label{tab:var-coverage}
\end{table}

The quality of estimation of $\Sigma$ and $\text{ESS}$ is assessed by running plots from 50 replications of run length 50000. 
 In Figure~\ref{fig:var-frob_n_ess}, we present running plots of $\log(\|\hat{\Sigma}\|_F)$ for both $\hat{\Sigma}_G$ and $\hat{\Sigma}_A$ and the running plots of $\log(\widehat{\text{ESS}})$ for both  $\widehat{\text{ESS}}_G$ and $\widehat{\text{ESS}}_A$. It is evident that the locally centered estimator of $\Sigma$ severely underestimates the truth, leading to an overestimation of ESS. The G-SV estimator is able to estimate $\Sigma$ more accurately early on, safeguarding against early termination using ESS. 
\begin{figure}[htbp]
    \centering
      \includegraphics[width = 2.0in]{plots/var-frob.pdf} 
      \includegraphics[width = 2.0in]{plots/var-ess.pdf}         
    \caption{VAR(1). (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV.(Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV.}
    \label{fig:var-frob_n_ess}
\end{figure}

@@

\begin{align*}
\hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t \in I_k} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
    &= \left[\dfrac{1}{n} \sum_{t \in I_k} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t \in J_{k2}} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right] \\ 
    & \quad +  \left[\dfrac{1}{n} \sum_{t \in J_{k1}}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right] + \left[\dfrac{n-\abs{k}}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
    &= \hat{\Gamma}_s(k) - \dfrac{1}{n} \sum_{t \in J_{k2}}^{k}A_{st}^T - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
\end{align*}
%
where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$. Under the assumption of stationarity, we will study the expectations of each of the above terms. Without loss of generality, consider $A_{11}$,
\begin{align*}
    &\E \left[A_{11} \right]\\
     &= \mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
     % &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
    % &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,. \numberthis \label{eq:acf_2}
\end{align*}
%
Similarly,
%    
\begin{align}
\label{eq:acf_3}
    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k)^T - n\text{Var}\left[\bar{X}_1 \right] \right)\,.
    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
\end{align}

Further,
\begin{align*}
\mathbb{E}\left[ \left(\bar{X}_{1} - \bar{\bar{X}} \right)  \left(\bar{X}_{1} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{X}_{1}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{1}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
&= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
\end{align*}
%
Additionally, the locally-centered autocovariance exhibits the following expectation (from \cite{priestley1981spectral})
 \begin{equation} \label{eq:priestly}
     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
 \right)\,.
 \end{equation}
%
Using\eqref{eq:acf_2}, \eqref{eq:acf_3}, \eqref{eq:acf_4}, and  \eqref{eq:priestly} in \eqref{eq:acf_breakdown},
\begin{align*}
    & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(\sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] + \sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}]\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
\end{align*}
%

@@

\begin{lemma} \label{lemma:G-SVE_breakdown}
For the G-SVE estimator, $\hat{\Sigma}_{G}^{ij} = \tilde{\Sigma}_A^{ij} + M_1 + M_2$ and 
\[
|M_1 + M_2| \leq D^2 g_1(n) + D g_2(n) + g_3(n)\,,
\]
where for some constant $C$,
\begin{align*}
    g_1(n) &= (4+C)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2} \to 0\\
    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4+C)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right] \to 0\,.
\end{align*}
\end{lemma}

@@

    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\left[ \dfrac{1}{n}\left|\sum_{t \in I_k}(Y_{st}- \mu_g)_i\right|\left|(\mu_g-\bar{\bar{Y}})_j\right|+ \dfrac{1}{n}\left|(\mu_g-\bar{\bar{Y}})_i\right|\left|\sum_{t \in I_k }(Y_{j(t+k)}-\mu_g)_j\right|\right]\right\}\\
    & \leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in I_k}(Y_{st}-\mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in I_k}(Y_{s(t+k)}-\mu_g)\right\|_{\infty} \right]\\
    &\leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \\

@@

    &\leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g)\right\|_{\infty} + 2\|\bar{Y}_s - \mu_g\|_{\infty} \right]\\
    & \leq \dfrac{\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum_{k=-b_n + 1}^{b_n-1}   \dfrac{1}{n}\left[\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g)\right\|_{\infty} + \left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g)\right\|_{\infty} \right]\\
    & \; \;+ 2(2b_n - 1)\|\bar{\bar{Y}} - \mu_g\|_{\infty}\|\bar{Y}_h - \mu_g\|_{\infty} \textrm{ for some } h \in \{1, \dots, m\} \,.

@@

    & < 2\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right]  + (2b_n - 1) \|\bar{Y}_h - \mu_g\|_{\infty}  \right]\\
    &\leq 2(2b_n - 1)\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n} + \|\bar{Y}_h - \mu_g\|_{\infty}  \right]\\

@@

    & \leq 4(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2  \quad \text{(by \eqref{eq:xbars_bound} and \eqref{eq:xbarbar_bound})}\,. \numberthis \label{eq:strong_consis_term-1}

@@

    g_1(n) &= (8 + C)\dfrac{b_n \psi^2(n)}{n^2} - 4\dfrac{\psi^2(n)}{n^2}\\
    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(8 + C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(8 + C)\dfrac{b_n \log\log n}{n} - 4 \dfrac{\log \log n}{n}\right]\,.

@@

    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left\|\sum_{t \in J_{k1}} \left(Y_{st} - \mu_g\right) \right\| + \dfrac{1}{m}\sum\limits_{s=1}^{m} \dfrac{cb_n(b_n-1)}{n} \left \|\bar{Y}_s - \mu_g \right \|_{\infty}^2\,.

@@

This is a 7-dimensional estimation problem wherein the marginal distribution of majority of components display a multimodal nature. Figure~\ref{fig:poisson-trace} shows the evolution of two chains started from random points with time for the second and third component. We will report the ACF plots for component-2. Similar behavior is observed for ACF plots of other components as well.

>>>>

\onehalfspacing
\begin{abstract}
Autocovariances are the fundamental quantity of interest in many features of Markov chain Monte Carlo (MCMC) simulations with autcorrelation function (ACF) plots being often used as a visual tool to ascertain the performance of a Markov chain. Unfortunately, for slow mixing Markov chains, the empirical autocovariance can highly underestimate the truth. For multiple chain MCMC sampling,  we propose a globally-centered estimator of autocovariance function (G-ACvF) that pools information from all Markov chains. G-ACvF is also shown to correct the negative bias of single chain empirical autocovariance. We show the impact of this improved estimator in three aspects: (1) ACF plots, (2) estimates of the Monte Carlo asymptotic covariance matrix, and (3) estimates of the effective sample size. We also establish the strong consistency of our improved asymptotic covariance estimator under weak conditions, and obtain its large sample bias and variance. 
\end{abstract}

@@

In this section we consider three different target distributions and sample $m$ parallel Markov chains using MCMC methods to experimentally analyse the performance of our globally-centered estimators. We will make the following three comparisons - (1) ACF vs G-ACF estimator, (2) SV vs G-SV estimator, and (3) $\widehat{\textrm{ESS}}_A$ vs $\widehat{\textrm{ESS}}_G$. The quality of estimation of $\Sigma$ is studied by coverage probabilities of a $95 \%$ Wald  confidence interval in cases where the true mean $\mu$ is known. The convergence of local and global estimators of $\Sigma$ and $\widehat{\textrm{ESS}}$ as $n$ increases is studied through two types of running plots (1) logarithm of Frobenius norm of estimated $\Sigma$, and (2) logarithm of estimated ESS/$mn$. In all the examples we are interested in estimating the mean of the stationary distribution $\mu$, so $g$ is the identity function. The batch size $b_n$ is obtained from the function \texttt{batchSize} from \texttt{R} package \texttt{mcmcse} \citep{mcmcse}.

@@

\begin{table}[htbp]
    \centering
    \small
    \begin{tabular}{|c|ccccc|}
    \hline
$n$  &  1000  & 5000  & 10000  & 50000  & 100000 \\  \hline
A-SV  &    0.710 & 0.843 & .885 & .928 & .944 \\ 
G-SV  &    0.956 & 0.937 & .924 & .945 & .952 \\ \hline
    \end{tabular}
    \caption{VAR(1). Coverage probabilities at $95 \%$ nominal level using A-SV and G-SV estimator.}
    \label{tab:var-coverage}
\end{table}

The quality of estimation of $\Sigma$ and $\text{ESS}$ is assessed by running plots from 50 replications of run length 50000. 
 In Figure~\ref{fig:var-frob_n_ess}, we present running plots of $\log(\|\hat{\Sigma}\|_F)$ for both $\hat{\Sigma}_G$ and $\hat{\Sigma}_A$ and the running plots of $\log(\widehat{\text{ESS}})$ for both  $\widehat{\text{ESS}}_G$ and $\widehat{\text{ESS}}_A$. It is evident that the locally centered estimator of $\Sigma$ severely underestimates the truth, leading to an overestimation of ESS. The G-SV estimator is able to estimate $\Sigma$ more accurately early on, safeguarding against early termination using ESS. 
\begin{figure}[htbp]
    \centering
      \includegraphics[width = 2.0in]{plots/var-frob.pdf} 
      \includegraphics[width = 2.0in]{plots/var-ess.pdf}         
    \caption{VAR(1). (Left) Running plot for logarithm of Frobenius norm of A-SV and G-SV estimator. (Right) Running plot for logarithm of $\widehat{\textrm{ESS}}/mn$ using A-SV and G-SV estimator.}
    \label{fig:var-frob_n_ess}
\end{figure}

@@

\begin{align*}
\hat{\Gamma}_{G,s}(k) & = \dfrac{1}{n}\sum_{t \in I_k} \left(X_{st} - \bar{\bar{X}} \right) \left(X_{s(t+k)} - \bar{\bar{X}} \right)^T \\
    &= \left[\dfrac{1}{n} \sum_{t \in I_k} \left(X_{st} - \bar{X}_s \right) \left(X_{s(t+k)} - \bar{X}_s \right)^T \right] + \left[\dfrac{1}{n} \sum_{t \in J_{k1}}  \left( \bar{X}_s - X_{st} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\ 
    & \quad + \left[\dfrac{1}{n} \sum_{t \in J_{k2}} \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - X_{st} \right)^T\right]   + \left[\dfrac{n-\abs{k}}{n} \left(\bar{X}_s - \bar{\bar{X}}\right)   \left(\bar{X}_s - \bar{\bar{X}} \right)^T\right]\\
    &= \hat{\Gamma}_s(k) - \dfrac{1}{n}\sum_{t \in J_{k1}}A_{st} - \dfrac{1}{n} \sum_{t \in J_{k2}}^{k}A_{st}^T  + \dfrac{n-\abs{k}}{n}  \left(\bar{X}_s - \bar{\bar{X}} \right)  \left(\bar{X}_s - \bar{\bar{X}} \right)^T\,, \numberthis \label{eq:acf_breakdown}
\end{align*}
%
where $A_{st} = (X_{st}-\bar{X}_s)(\bar{X}_s - \bar{\bar{X}})^T$. Under the assumption of stationarity, we will study the expectations of each of the above terms. Without loss of generality, consider $A_{11}$,
\begin{align*}
    &\E \left[A_{11} \right]\\
     &= \mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
     % &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
    &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
    &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
    % &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
    &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,. \numberthis \label{eq:acf_2}
\end{align*}
%
Similarly,
%    
\begin{align}
\label{eq:acf_3}
    \mathbb{E} \left[ A_{11}^T \right] &= \mathbb{E}\left[ A_{11}\right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k)^T - n\text{Var}\left[\bar{X}_1 \right] \right)\,.
    % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
\end{align}

Further,
\begin{align*}
\mathbb{E}\left[ \left(\bar{X}_{1} - \bar{\bar{X}} \right)  \left(\bar{X}_{1} - \bar{\bar{X}} \right)^{T}\right] &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{X}_{1}\bar{\bar{X}}^{T} - \bar{\bar{X}} \bar{X}_{1}^{T} + \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \mathbb{E}\left[ \bar{X}_{1}\bar{X}_{1}^{T} - \bar{\bar{X}}\bar{\bar{X}}^{T}\right]\\
% &= \left(\mathbb{E}\left[\bar{X}_{1}\bar{X}_{1}^{T}\right] - \mathbb{E}\left[\bar{\bar{X}}\bar{\bar{X}}^{T}\right]\right)\\
&= \left(\Var(\bar{X}_{1}) + \mu\mu^{T} - \Var(\bar{\bar{X}}) - \mu\mu^{T}\right)\\
&= \dfrac{m-1}{m}\Var(\bar{X}_1)\,. \numberthis \label{eq:acf_4}
\end{align*}
%
Additionally, the locally-centered autocovariance exhibits the following expectation (from \cite{priestley1981spectral})
 \begin{equation} \label{eq:priestly}
     \mathbb{E}[\hat{\Gamma}(k)] = \left(1- \dfrac{\abs{k}}{n}\right)\left(\Gamma(k) - \Var{(\bar{X})}
 \right)\,.
 \end{equation}
%
Using\eqref{eq:acf_2}, \eqref{eq:acf_3}, \eqref{eq:acf_4}, and  \eqref{eq:priestly} in \eqref{eq:acf_breakdown},
\begin{align*}
    & \E \left[\hat{\Gamma}_{G,s}(k) \right] \\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{1}{n} \left(+ \sum\limits_{t \in J_{k1}}\mathbb{E}[A_{1t}] + \sum\limits_{t \in J_{k2}}\mathbb{E}[A_{1t}^T] \right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \mathbb{E}\left[\hat{\Gamma}_{s}(k)\right] - \dfrac{\abs{k}}{n}\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h) + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T - 2 \Var(\bar{X}_1)\right) + \left(1- \dfrac{\abs{k}}{n}\right)\left(1-\dfrac{1}{m}\right)\Var(\bar{X}_1)\\
    &= \left(1- \dfrac{\abs{k}}{n}\right)\Gamma(k) - \dfrac{\abs{k}}{n}\left[\left(1-\dfrac{1}{m}\right)\left(\dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)^T + \dfrac{1}{n}\sum_{h=0}^{n-1}\Gamma(h)\right) - \left(2-\dfrac{1}{m}\right) \Var(\bar{X}_1)\right] - \dfrac{\Var(\bar{X}_1)}{m}\,.
\end{align*}
%

@@

\begin{lemma} \label{lemma:G-SVE_breakdown}
Let Assumption~\ref{ass:lag_window} holds, then for the G-SV estimator, $\hat{\Sigma}_{G}^{ij} = \tilde{\Sigma}_A^{ij} + M_1 + M_2$ and 
\[
|M_1 + M_2| \leq D^2 g_1(n) + D g_2(n) + g_3(n)\,,
\]
where for some constant $C$,
\begin{align*}
    g_1(n) &= (4c+C)\dfrac{b_n \psi^2(n)}{n^2} - 4c\dfrac{\psi^2(n)}{n^2} \to 0\\
    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(4c+C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4c\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right] \to 0\\
    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(4c+C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right] \to 0\,.
\end{align*}
\end{lemma}

@@

    & \leq \dfrac{1}{m}\sum_{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}\abs{w\left(\dfrac{k}{b_n}\right)}\left[ \dfrac{1}{n}\left|\sum_{t \in I_k}(Y_{st}- \mu_g)_i\right|\left|(\mu_g-\bar{\bar{Y}})_j\right|+ \dfrac{1}{n}\left|(\mu_g-\bar{\bar{Y}})_i\right|\left|\sum_{t \in I_k }(Y_{j(t+k)}-\mu_g)_j\right|\right]\right\}\\
    & \leq \dfrac{c\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in I_k}(Y_{st}-\mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in I_k}(Y_{s(t+k)}-\mu_g)\right\|_{\infty} \right]\\
    &\leq \dfrac{c\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \\

@@

    &\leq \dfrac{c\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum_{s=1}^{m}\sum\limits_{k=-b_n+1}^{b_n-1}\left[ \dfrac{1}{n}\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g)\right\|_{\infty} + \dfrac{1}{n}\left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g)\right\|_{\infty} + 2\|\bar{Y}_s - \mu_g\|_{\infty} \right]\\
    & \leq \dfrac{c\|(\bar{\bar{Y}} - \mu_g)\|_{\infty}}{m} \sum\limits_{s=1}^{m}\sum_{k=-b_n + 1}^{b_n-1}   \dfrac{1}{n}\left[\left\|\sum_{t \in J_{k1}}(Y_{st} - \mu_g)\right\|_{\infty} + \left\|\sum_{t \in J_{k2}}(Y_{st} - \mu_g)\right\|_{\infty} \right]\\
    & \; \;+ 2c(2b_n - 1)\|\bar{\bar{Y}} - \mu_g\|_{\infty}\|\bar{Y}_h - \mu_g\|_{\infty} \textrm{ for some } h \in \{1, \dots, m\} \,.

@@

    & < 2c\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[\sum\limits_{k=-b_n + 1}^{b_n-1}\left[ \dfrac{D \psi(k)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{2k \log\log k}}{n}  \right]  + (2b_n - 1) \|\bar{Y}_h - \mu_g\|_{\infty}  \right]\\
    &\leq 2c(2b_n - 1)\|(\bar{\bar{Y}} - \mu_g)\|_{\infty} \left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n} + \|\bar{Y}_h - \mu_g\|_{\infty}  \right]\\

@@

    & \leq 4c(2b_n - 1)\left[ \dfrac{D \psi(n)}{n} + \dfrac{\|L\| p^{1/2}(1+\epsilon)\sqrt{n \log\log n}}{n}  \right]^2  \quad \text{(by \eqref{eq:xbars_bound} and \eqref{eq:xbarbar_bound})}\,. \numberthis \label{eq:strong_consis_term-1}

@@

    g_1(n) &= (8c + C)\dfrac{b_n \psi^2(n)}{n^2} - 4c\dfrac{\psi^2(n)}{n^2}\\
    g_2(n) &= 2\sqrt{2}\|L\|p^{1/2}(1+\epsilon)\left[(8c + C)\dfrac{b_n\psi(n)\sqrt{n\log \log n}}{n^2} - 4c\dfrac{\psi(n)\sqrt{n\log \log n}}{n^2}\right]\\
    g_3(n) &= \|L\|^2 p (1+\epsilon)^2\left[(8c + C)\dfrac{b_n \log\log n}{n} - 4c \dfrac{\log \log n}{n}\right]\,.

@@

    & \leq \dfrac{c}{m}\sum_{s=1}^{m}\sum_{k=-b_n+1}^{b_n-1}\dfrac{\|\bar{Y}_s - \mu_g\|_{\infty}}{n} \left\|\sum_{t \in J_{k1}} \left(Y_{st} - \mu_g\right) \right\| + \dfrac{c}{m}\sum\limits_{s=1}^{m} \dfrac{b_n(b_n-1)}{n} \left \|\bar{Y}_s - \mu_g \right \|_{\infty}^2\,.

@@

This is a 7-dimensional estimation problem wherein the marginal distribution of majority of components display a multimodal nature. Figure~\ref{fig:poisson-trace} shows the evolution of two chains started from random points with time for the second and third component. We report the ACF plots for the second component component only, however, similar behavior is observed in ACF plots of other components as well.
